---
title: "Alcohol vs Seat choice"
author: "Juan Moreno"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

According to the data chart, people who drink more are   the ones in the back seat, while people in the front   will drink less, which is logical since its illegal to   drink and drive.  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

In the table above, it shows that there are more people   sitting in the middle row then any other row, meaning   that they will consume more alchohol than any other   group.    

## Inferential Tests



## Conclusions


